Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-01 draft.tex

>>>>

\section{Universal bulk TFT}
\label{sec: TFT}

Generally speaking, the local observables of a topological field theory on a manifold $M$ define a locally constant factorization algebra on $M$.

\begin{thm}
Let $M$ be a smooth $n$-manifold and $\fg$ a Lie algebra. 
There is a constructible factorization algebra on $M \times [0,1)$ satisfying the following properties:
\begin{itemize}
\item[(1)] On the $n$-dimensional stratum $M \times \{0\}$ the factorization algebra is equivalent to $\clieu (\fg \otimes \Omega_c)$.
\item[(2)] On the $(n+1)$-dimensional stratum $M \times (0,1)$, the factorization algebra is a quantization of the observables of topological BF theory based on the Lie algebra $\fg$.
\item[(3)] Locally on $\RR^n \times [0,1)$ this factorization algebra produces \brian{deligne picture how to say}
\end{itemize}
\end{thm}

%Let $\fg$ be a dg Lie algebra and consider the $E_n$ algebra $\UU_n \fg$. 
%We have shown that a model for the $E_n$-center ${\frak Z}_n (\UU_n \fg) = {\frak Z}_n ({\rm id}_{\UU_n \fg})$ is the $n$-dimensional locally constant factorization algebra 
%\[
%\clie \left( \fg \otimes \Omega \; , \; \clieu (\fg \otimes \Omega_c) \right)  .
%\]

\subsection{The bulk TFT}

Let us place the locally constant factorization algebra module the $E_n$-enveloping algebra $\clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
This factorization algebra is equivalent to the pushforward of a factorization algebra $\Obs_{\rm BF}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times (0,1) \to M$ which we proceed to construct.

\begin{dfn}
For an open set $V \subset M \times (0,1)$ let $\Obs^{\rm cl}_{\rm BF} (V)$ be the cochain complex 
\[
\Obs^{\rm cl}_{\rm BF} (V) = \clie \bigg(\fg \otimes \Omega (V) \; , \; \Sym \left(\fg \otimes \Omega_c(V) [2] \right) \bigg) .
\]
The assignment $V \mapsto \Obs^{\rm cl}_{\rm BF}(V)$ defines a locally constant factorization algebra on $M \times (0,1)$. 
\end{dfn}

We note that $\Obs_{\rm BF}^{\rm cl}$ is a factorization algebra with values in commutative dg algebras. 
In fact, it is given by the ``classical observables" of a topological field theory on $M \times (0,1)$ known as ``topological BF theory".

We now consider the pushforward factorization algebra $\pi_* \Obs^{\rm cl}_{\rm BF}$ on $M$.
Locally, on disks, we will see that it is quasi-isomorphic to a certain limit, or ``dequantization", of our model for the $E_n$-center of $\UU_n \fg$.
Recall, this model is given by the factorization algebra on $M$:
\begin{equation}\label{eqn:centerTFT}
\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) .
\end{equation}

The ``dequantization" is defined using the following filtration of this model.
For any Lie algebra $\fh$, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space.

\begin{dfn}
Introduce the filtration on the factorization algebra on $M$ in (\ref{eqn:centerTFT}) by 
\[
F^k \bigg(\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) \bigg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
\]
\end{dfn}

This is a filtration of factorization algebras on $M$. 
The associated graded factorization algebra is
\[
{\rm Gr} \; \bigg(\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) \bigg) \; = \; \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
\]
Notice this is similar to the model $E_n$-center except we have turned off the Chevalley--Eilenberg differential on chains.

 \begin{lmm}
There is a quasi-isomorphism of commutative factorization algebras on $M$:
\[
\pi_* \Obs^{\rm cl}_{\rm BF} \; \xto{\simeq} \; {\rm Gr} \; \bigg(\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) \bigg) .
\]
\end{lmm}

In fact, we will show that this quasi-isomorphism is a deformation retraction.

\begin{proof}
To exhibit this quasi-isomorphism, we introduce the following cochain maps.
For an open set $U \subset M$ let
\[
\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
\] 
be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
\[
r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
\]
by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
\end{proof}

\section{Factorization algebras that model centralizers}

\brian{Remark about twisting in the unoriented case.}
